Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-28 hscc2017/paper.tex
Review conclusions to make the contributions clearer (https://github.com/kroening/control-synthesis/issues/48)

We have presented a CEGIS-based approach implemented in a tool called \tool,
which uses inductive synthesis in conjunction with an algorithm for
verifying robust closed-loop stability.  In particular, \tool is able to
compute a parametric solution for a stabilizing digital controller given a
continuous (or discrete) plant specification.  This enables us to
automatically synthesize correct-by-construction digital controllers for a
given model of their physical environment.  Our approach addresses the
effects of the quantizers (A/D and D/A converters) as time discretization
elements with quantization noise.  Our experimental results show that \tool
is able to synthesize stable controllers in most benchmarks within
a reasonable amount of time fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.

Future work will be the extension of this CEGIS-based approach to further
classes of systems, including state-space representation.  We will also
consider performance requirements while synthesizing the digital controller.

>>>>

We have presented a CEGIS-based approach implemented in a tool 
called \tool, which uses inductive synthesis in conjunction with 
an algorithm for verifying robust closed-loop stability that addresses 
plant variations as interval sets as well as FWL uncertainties in digital 
controllers. The present approach is novel in the control system 
literature in that it puts forward a fully automated synthesis approach that 
is algorithmically and numerically sound. In particular, \tool marks the first 
use of the CEGIS paradigm, which handles plants with uncertain models and 
FWL effects over the digital controller.  Note that implementing this architecture 
efficiently requires adjusting the traditional CEGIS refinement loop to the use 
of a two-stage verification engine: here the first stage performs fast, but potentially 
unsound fixed-point operations, whereas the second stage restores soundness 
by validating the operations performed by the first stage using interval 
arithmetic. Our experimental results show that \tool
is able to synthesize stable controllers in most benchmarks within
a reasonable amount of time fully automatically.  Future work will be the 
extension of this CEGIS-based approach to further classes of systems, 
including state-space.  We will also consider performance 
requirements while synthesizing the digital controller.
